Type Ia Supernova Explosions from Hybrid Carbon-Oxygen-Neon White Dwarf Progenitors

### 2017-08-02 paper/ms.tex
Added the citation to the 2nd Brooks paper.
Added citation to Willcox et al. 2016.

@@

Summarize what we do a la:
In our simulations, we
initialize a detonation once the deflagration front reaches a
characteristic DDT fuel density, which controls the degree of
expansion the star undergoes during the deflagration stage. The
implementation details are described further in
\secref{subsec:ddt_details}.

>>>>

Here's the other Books paper \citep{brookset2017}. Do we need to mention it?
Give a read to see!

@@

Summarize what we do a la:
In our simulations, we initialize a detonation once the 
deflagration front reaches a
characteristic DDT fuel density, which controls the degree of
expansion the star undergoes during the deflagration stage.

The comparison study of tradition C/O progentor WDs used the same
initial conditions for the realizations within the suite. Make the
point that the traditional models are simalted with the same code
and the same set if perturbations on the initial match head (that is
what we mean by a realization). The only difference is the different
nuclear buring to include the other Ne and the initial profile of
the 1-d model.

For much of the methodology to be described below, just say a few
words about what was done and cite \citet{willcoxetal2016}.
